\documentclass[Bachelor, BIF, english, table]{twbook}

\usepackage[T1]{fontenc}
%%\usepackage[ansinew]{inputenc}
\usepackage[utf8]{inputenc}
% Die nachfolgenden 2 Pakete stellen sonst nicht benötigte Features zur Verfügung
%%\usepackage{blindtext,dtklogos}
\usepackage{blindtext, dtk-logos}
\usepackage{cite}

%-------------------------------- for algorithms
%\usepackage{fullpage}
%\usepackage{times}
%\usepackage{fancyhdr,graphicx,amsmath,amssymb}
%\usepackage[ruled,vlined]{algorithm2e}
%\include{pythonlisting}


\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%--------------------------------

%-------------------------------- for code highlighting
\usepackage{minted}
%\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.9}
\usemintedstyle{borland}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
%--------------------------------
\usepackage{physics}


%-------------------------------- for commenting
%--- https://tex.stackexchange.com/questions/9796/how-to-add-todo-notes
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
% \usepackage[pdftex,dvipsnames]{xcolor}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
% \newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
%\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
%-------------------------------- 


%-------------------------------- for UML
\usepackage[]{pgf-umlcd}

%-------------------------------- 
\usepackage{multirow}
\usepackage{booktabs}
\providecommand*{\listingautorefname}{Listing}

%-------------------------------- for highlighting
\usepackage{soul}

\title{Anomaly detection in data for data cleansing}
% \extratitle{Der Untertietel}
\author{David Zelenay}
\studentnumber{000000000000}
\supervisor{Degree First Name Surname}
\place{Vienna}
\kurzfassung{
    % TODO Add Kurzfassung
    Diese Bachelorarbeit befasst sich mit dem Thema Anomalie-Erkennung, mit einem Fokus auf Ausreißererkennung. Der Einstig bildet ein Überblick welche Merkmale Datenqualität ausmachen. Danach werden einige Methoden zur Erkennung von Ausreißern vorgestellt. Diese Methoden werden dann mit Daten aus der echten Welt getestet. Die Daten sind Wasserstandsdaten von Flüssen, welche verwendet werden, um Fluten rechtzeitig zu erkennen und betroffene Personen zu warnen. Bevor die Modelle mit den Daten getestet werden, wurde noch eine explorative Datenanalyse durchgeführt, um sich einen Überblick über die Daten zu verschaffen. Am Schluss werden die Ergebnisse der verschiedenen Ansätze Ausreißer zu erkennen verglichen und ausgewertet. Um die Ergebnisse verlgeichen zu können wurde eine passende Kennzahl definiert, welche auskunft über die Leistung des Modells gibt.
    \change{Change this}
}
\outline{
    % TODO add Abstract
    % \todo{Change this}
    This bachelor thesis analyzes methods for anomaly detection, with a focus on outlier detection for time series data. In the beginning an overview of the characteristics that make up data quality are outlined. Afterwards some methods for outlier detection are presented. These Methods are then tested with real world data. The data used for testing consists of the water levels of different rivers, this data is originally used to warn people about upcoming floods in their area of interest. However before testing the models with the data, an explorative data analysis was conducted to provide an overview of the data. At the end, the results of the different approaches to detect outliers are compared and evaluated. In order to be able to compare the models, a suitable performance metric was defined.
    
    \change{change this}
    % This paper analyzes methods for anomaly detection to cleanse data. An overview of some key features of data quality is provided in the beginning. The difference between data cleaning and data cleansing is elaborated. Additionally a few methods for anomaly detection (mainly outlier detection) are outlined. The hypothesis of this paper is: Which characteristics define data quality, with regard to \ac{IoT} Sensors? Which methods are there to detect and clean or cleanse faulty data?
}
\begin{document}
\maketitle
% \include{chapters/structure.tex}
% \showthe\textwidth
% 418.25555pt 
\change{Change title to: ``Anomaly detection for time series data''?}
\include{overview} 
\include{dataQuality} 
\include{outlierDetection}
\include{waterLevelOutlierDetection}
\include{conclusion}
\include{appendix}
\include{backmatter}

\end{document}